Squintability and Other Metrics for Assessing Projection Pursuit Indexes, and Guiding Optimisation Choices

### 2025-02-11 jso.qmd
update sec 5

In addition, to assess the performance of JSO across various PP problems, two different
data shapes, pipe and a sine wave, are studied in 4D, 6D and 8D spaces
using six different PP indexes: `dcor2d_2`, `loess2d`, `MIC`, `TIC`,
`spline`, and `stringy`, under varied JSO hyper-parameters. This results
in a total of `r nrow(sim_df)` scenarios, comprising of
`r nrow(filter(sim_df, index == "holes"))` computed on the pipe data and
`r nrow(filter(sim_df, index != "holes"))` on the sine-wave data. Again,
JSO is run 50 times for each scenario to calculate the success rate for
each PP problem.

>>>>

In addition, to assess the performance of JSO across various PP problems, two different
data shapes, pipe and a sine wave, are considered in various dimensional spaces
using six different PP indexes: `dcor2d_2`, `loess2d`, `MIC`, `TIC`,
`spline`, and `stringy`, under varied JSO hyper-parameters. This results
in a total of `r nrow(sim_df)` scenarios, comprising of
`r nrow(filter(sim_df, index == "holes"))` computed on the pipe data and
`r nrow(filter(sim_df, index != "holes"))` on the sine-wave data. A list of combinations of the data shape, dimensions and PP indexes considered are provided in @tbl-smoothness-squintability. Again, JSO is run 50 times for each scenario to calculate the success rate for each hyper-parameter combination.
